Oral anticoagulants

### 2021-01-17 r_notebooks/exploring_oral_anticoagulants_war_prop.Rmd
R analyses

  # Fable models will run using plan(multisession), but need to be run as below
  # with `furrr_options(seed = TRUE)` otherwise improper random numbers are
  # generated
  fable_fits <-
    future_map_dfr(.x =  regions,
                   .f = ~fableCV(data = filter(data, regional_unit == .x)),
                   .options = furrr_options(seed = TRUE))
  message("fableModelsBound() complete")

@@

  fable_fit <-
    future_map_dfr(.x = regions,
                   .f = ~fableModelsBound(filter(data, regional_unit ==.x)) %>%
                    forecast(h = h),
                   .options = furrr_options(seed = TRUE)) %>%
    as_tibble()

@@

  prophet_fit <-
    future_map_dfr(.x = regions,
                   .f = ~prophetModelsBound(filter(data, regional_unit ==.x)) %>%
                    forecast(h = h),
                   .options = furrr_options(seed = TRUE)) %>%
    as_tibble()

@@

```{r, health-board-modelling}
plan(multisession)
system.time(oac_p_hb_cv_models <-
  regionalCV(data = oac_p_monthly_quantity_hb_pre_cv19))
plan(sequential)
oac_p_hb_cv_models %>%
  write_rds("../data/oac_p_hb_cv_models.rds")

@@

* 724.044 seconds with multisession prophetModelsBound()
* 418.410 seconds with neur_net removed 2021-01-11

@@

oac_p_hb_fcsts <- 
  read_rds("../data/oac_p_hb_fcsts.rds")
```

* 194.071 seconds 2020-12-10
* 71.559 seconds 2021-01-11

@@

```{r, gp-cluster-modelling}
plan(multisession)
system.time(oac_p_gp_cluster_cv_models <-
  regionalCV(data = oac_p_monthly_quantity_cluster_pre_cv19))
plan(sequential)

@@

* 5514.279 seconds
* 2059.159 seconds 2021-01-11

@@

* 2.195e+04 seconds 2020-12-07
* 25547.266 seconds 2020-12-09

@@

>>>>

  # Fable models will run using plan(cluster), but need to be run as below
  # with `furrr_options(seed = TRUE)` otherwise improper random numbers are
  # generated
  fable_fits <-
    future_map_dfr(.x =  regions,
                   .f = ~fableCV(data = filter(data, regional_unit == .x)),
                   .options = furrr_options(seed = TRUE))
  message("fableModelsBound() complete")

@@

  fable_fcst <-
    future_map_dfr(.x = regions,
                   .f = ~fableModelsBound(filter(data, regional_unit ==.x)) %>%
                    forecast(h = h),
                   .options = furrr_options(seed = TRUE)) %>%
    as_tibble()

@@

  prophet_fcst <-
    future_map_dfr(.x = regions,
                   .f = ~prophetModelsBound(filter(data, regional_unit ==.x)) %>%
                    forecast(h = h),
                   .options = furrr_options(seed = TRUE)) %>%
    as_tibble()

@@

```{r, health-board-modelling}
plan(cluster)
system.time(oac_p_hb_cv_models <-
  regionalCV(data = oac_p_monthly_quantity_hb_pre_cv19))
plan(sequential)
oac_p_hb_cv_models %>%
  write_rds("../data/oac_p_hb_cv_models.rds")

@@

* 965.17 seconds with prophetModelsBound() 2021-01-15

@@

oac_p_hb_fcsts <- 
  read_rds("../data/oac_p_hb_fcsts.rds")
```
129.80 2021-01-15
*

@@

```{r, gp-cluster-modelling}
plan(cluster)
system.time(oac_p_gp_cluster_cv_models <-
  regionalCV(data = oac_p_monthly_quantity_cluster_pre_cv19))
plan(sequential)

@@

*

@@

* prophetModelsBound() complete
NaNs producedfableModelsBound() complete
    user   system  elapsed 
  504.83    38.03 11465.09 
prophetModelsBound() complete                                         
NaNs producedNaNs producedfableModelsBound() complete                 
    user   system  elapsed 
  520.35    40.97 11534.13 
prophetModelsBound() complete
fableModelsBound() complete
    user   system  elapsed 
  377.34    22.89 11300.13 
prophetModelsBound() complete
fableModelsBound() complete
    user   system  elapsed 
  370.35    21.11 11321.84

@@

oac_p_gp_fcsts <-
  read_rds("../data/oac_p_gp_fcsts.rds")
